\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-05-09 msnbase2.Rnw
use [MB] - close #13

p_sz <- 
    data.frame(sz) %>% 
    rownames_to_column() %>% 
    pivot_longer(names_to = "files", 
                 values_to = "size",
                 -rowname) %>% 
    rename(backend = rowname) %>% 
    mutate(files = as.numeric(sub("X", "", files))) %>% 
    ggplot(aes(x = files, y = size, colour = backend)) + 
    geom_point() + 
    geom_line() + 
    scale_x_continuous(breaks=c(1, 5, 10)) + 
    ylab("Object size (MB)") +
    xlab("Number of files") +
    theme(legend.position = "none")    
@

>>>>

p_sz <- 
    data.frame(sz) %>% 
    rownames_to_column() %>% 
    pivot_longer(names_to = "files", 
                 values_to = "size",
                 -rowname) %>% 
    rename(backend = rowname) %>% 
    mutate(files = as.numeric(sub("X", "", files))) %>% 
    ggplot(aes(x = files, y = size, colour = backend)) + 
    geom_point() + 
    geom_line() + 
    scale_x_continuous(breaks=c(1, 5, 10)) + 
    ylab("Object size [MB]") +
    xlab("Number of files") +
    theme(legend.position = "none")    
@
